---
title: "Advanced PLS-SEM Analysis"
author: "Asif Rahman"
---

```{r}
library(seminr)

```

```{r}
# Load the influencer data


library(readr)

influencer_data <- read_csv("Influencer_data.csv")

View(influencer_data)

```

```{r}

# Show the first several rows of the influencer data

head(influencer_data)

```
#------------------------------------------------------------------------------
```{r}

# Summary of the influencer data

summary(influencer_data)

```


```{r}
# * REFLECTIVE MEASUREMENT MODEL *

```

```{r}

# Create measurement model

simple_mm <- constructs(
  composite("PL", multi_items("pl_", 1:4)),
  composite("PIC", multi_items("pic_", 1:5)),
  composite("PI", multi_items("pi_", 1:5)),
  composite("WTP", single_item("wtp")),
  composite("PQ", multi_items("pq_", 1:4))
  )

```

```{r}

plot(simple_mm)

```

```{r}
# Create structural model

simple_sm <- relationships(
  paths(from = c("PL","PQ","PIC"), to = "PI"),
  paths(from = "PI", to = "WTP"))

```

```{r}

plot(simple_sm, theme= seminr_theme_old())

```

```{r}
# Estimate the model

influencer_simple_model <- estimate_pls(data = influencer_data,
                                      measurement_model = simple_mm,
                                      structural_model = simple_sm,
                                      inner_weights = path_weighting,
                                      missing = mean_replacement,
                                      missing_value = "-99")
```

```{r}
# Summarize the model results

summary_simple_influencer <- summary(influencer_simple_model)

summary_simple_influencer
```

```{r}

# Inspect the model’s path coefficients and the R^2 values

summary_simple_influencer$paths

```

```{r}
# Inspect the composite reliability

summary_simple_influencer$reliability

```
# All alpha, rhoC and rhoA exceeded 0.7 and AVE exceeded 0.5.
# All rhoA value exceeded the recommended value of 0.8 to 0.9.

```{r}
# Plot the model

plot(influencer_simple_model,title = "Asif Rahman - Mediation Analysis                                ")

```
```{r}
# Inspect the indicator lodgings:

summary_simple_influencer$loadings

```

```{r}
# Inspect the indicator reliability

summary_simple_influencer$loadings^2

```

```{r}

# Table of the FL criteria

summary_simple_influencer$validity$fl_criteria

```
```{r}

# HTMT criterion

summary_simple_influencer$validity$htmt

```
# * All HTMT values are < 0.9 or 0.85 *


# **Bootstrap The Model**

```{r}
# Bootstrap the model

boot_simple_influencer <- bootstrap_model(seminr_model = influencer_simple_model,
                                        nboot = 1000,
                                        cores = NULL,
                                        seed = 123)
```

```{r}
# Store the summary of the bootstrapped model

sum_boot_simple_influencer <- summary(boot_simple_influencer)

sum_boot_simple_influencer

```

```{r}
#Extract The bootstrapped HTMT

sum_boot_simple_influencer$bootstrapped_HTMT

```
# All HTMT values are < 0.9 or 0.85. 

# And all CI are in positive side, that means they all are significant.


# ** Formative Measurement Model **


```{r}

# Create measurement model

influencer_mm <- constructs(
  composite("SIC", multi_items("sic_", 1:7), weights = mode_B),
  composite("PL", multi_items("pl_", 1:4)),
  composite("PIC", multi_items("pic_", 1:5)),
  composite("PI", multi_items("pi_", 1:5)),
  composite("WTP", single_item("wtp")),
  composite("PQ", multi_items("pq_", 1:4))
  )

```

```{r}
plot(influencer_mm)

```

```{r}
# Create structural model

influencer_sm <- relationships(
  paths(from = c("SIC","PL","PQ","PIC"), to = "PI"),
  paths(from = "PI", to = "WTP"),
  paths(from = "SIC", to = c("PL","PQ")))

```

```{r}
plot(influencer_sm, theme = seminr_theme_dark())
```

```{r}
# Estimate the model

influencer_model <- estimate_pls(data = influencer_data,
                                      measurement_model = influencer_mm,
                                      structural_model = influencer_sm,
                                      missing = mean_replacement,
                                      missing_value = "-99")
```

```{r}
# Summarize the model results
summary_influencer_model <- summary(influencer_model)
summary_influencer_model
```

```{r}
# Iterations to converge
summary_influencer_model$iterations
```

```{r}
# Bootstrap the model
boot_influencer <- bootstrap_model(seminr_model = influencer_model, nboot = 1000)
```

```{r}

# Summary of the model

sum_boot_influencer_model <- summary(boot_influencer, alpha = 0.10)

sum_boot_influencer_model

```


```{r}
# Extract the bootstrapped HTMT
sum_boot_influencer_model$bootstrapped_HTMT

```


#-------------------------------------------------------------

# * Redundancy Analysis *

```{r}
# SIC

# Create measurement model
SIC_redundancy_mm <- constructs(
  composite("SIC_F", multi_items("sic_", 1:7), weights = mode_B),
  composite("SIC_G", single_item("sic_global"))
)

plot(SIC_redundancy_mm)
```

```{r}

# Create structural model

SIC_redundancy_sm <- relationships(
  paths(from = c("SIC_F"), to = c("SIC_G"))
)

plot(SIC_redundancy_sm)

```

```{r}
# Estimate the model
SIC_redundancy_pls_model <- estimate_pls(
  data = influencer_data,
  measurement_model = SIC_redundancy_mm,
  structural_model = SIC_redundancy_sm,
  missing = mean_replacement,
  missing_value = "-99")
```

```{r}
# Summarize the model
sum_SIC_red_model <- summary(SIC_redundancy_pls_model)

sum_SIC_red_model

```


```{r}
# Check the path coefficients for convergent validity

sum_SIC_red_model$paths
```
# SIC_F = 0.717 and it is above the threshold. That means this
# formatively measured construct exhibits convergent validity.

```{r}

# Collinearity analysis

summary_influencer_model$validity$vif_items

```
# If VIF >= 5 , then critical collinearity issues likely occur.

# For example: pl_2, pi_5 etc.



# If VIF = 3 to 5 , then collinearity issues are usually uncritical.

# For example: sic_1, sic_2, pq_1, pi_4 etc.



# If VIF < 3, then collinearity is not a problemtic issue.

# For example: sic_4, sic_5, pl_4 etc.

```{r}
# Bootstrap the model

boot_influencer_ext <- bootstrap_model(
  seminr_model = influencer_model,
  nboot = 1000,
  cores = parallel::detectCores(),
  seed = 123)
```
# * Summarize the results of the bootstrap *

```{r}
# alpha sets the specified level for significance, i.e. 0.05

sum_boot_influencer_ext <- summary(boot_influencer_ext, alpha = 0.05)

```

```{r}
# Inspect the bootstrapping results for indicator weights

sum_boot_influencer_ext$bootstrapped_weights

```

# All are significant , except: sic_1, sic_3 to sic_7 and pic_1


# -------------------------------------------------------------

# *STRUCTURAL MODELING *

```{r}

# Create measurement model

influencer_mm_ext <- constructs(
  composite("SIC", multi_items("sic_", 1:7), weights = mode_B),
  composite("PL", multi_items("pl_", 1:4)),
  composite("PIC", multi_items("pic_", 1:5)),
  composite("PI", multi_items("pi_", 1:5)),
  composite("WTP", single_item("wtp")),
  composite("PQ", multi_items("pq_", 1:4))
  )

```


```{r}
# Create structural model

influencer_sm_ext <- relationships(
  paths(from = c("SIC","PL","PQ","PIC"), to = "PI"),
  paths(from = "PI", to = "WTP"),
  paths(from = "SIC", to = c("PL","PQ")))

```

```{r}
# Estimate the model
influencer_pls_ext <- estimate_pls(data = influencer_data,
                                      measurement_model = influencer_mm_ext,
                                      structural_model = influencer_sm_ext,
                                      missing = mean_replacement,
                                      missing_value = "-99")
```

```{r}
# Summarize the results of the model estimation

summary_influencer_ext <- summary(influencer_pls_ext)

```


```{r}
# Bootstrap the model

boot_influencer_ext_1 <- bootstrap_model(
  seminr_model = influencer_pls_ext,
  nboot = 1000,
  cores = parallel::detectCores(),
  seed = 123)
```

```{r}
# Summarize the results of the bootstrap
summary_boot_influencer_ext <- summary(boot_influencer_ext_1,
                                     alpha = 0.05)
```

```{r}
# Inspect the structural model collinearity VIF

summary_influencer_ext$vif_antecedents

```
# All VIF < 3, that means collinearity is not a problemtic issue.


```{r}
# Inspect the structural paths

summary_boot_influencer_ext$bootstrapped_paths
```
# All are significant. Except: SIC to PI, PQ to PI,PIC to PI.


```{r}
# Inspect the total effects

summary_boot_influencer_ext$bootstrapped_total_paths

```



```{r}
# Inspect the model RSquares

summary_influencer_ext$paths

```
# Here, R2 value of PI is moderate. Except that all are weak.

```{r}
# Inspect the effect sizes

summary_influencer_ext$fSquare

```
# Here is the f2 value. We can get the size effect with this.

```{r}
# Generate the model predictions
predict_influencer_ext <- predict_pls(
  model = influencer_pls_ext,
  technique = predict_DA,
  noFolds = 10,
  reps = 10)
```

```{r}
# Summarize the prediction results
sum_predict_influencer_ext <- summary(predict_influencer_ext)

sum_predict_influencer_ext
```

```{r}
# Analyze the distribution of prediction error

par(mfrow=c(1,5))
plot(sum_predict_influencer_ext,
     indicator = "pi_1")
plot(sum_predict_influencer_ext,
     indicator = "pi_2")
plot(sum_predict_influencer_ext,
     indicator = "pi_3")
plot(sum_predict_influencer_ext,
     indicator = "pi_4")
plot(sum_predict_influencer_ext,
     indicator = "pi_5")


par(mfrow=c(1,1))
```
# The result of the plots showed that, from left, 1,2 and 4 no. graphs

# have a right trail and they are skewed to the left.

# And the rest are symmetric.

```{r}
# Compute the prediction statistics

sum_predict_influencer_ext

```
# For example, pi_3 of PLS out of sample (1.413) < pi_3 LM out of sample (1.442)

# That means pi_3 LM out of sample has more predictive power.


# * Estimate alternative models *

```{r}

# Create measurement model

measurement_model <- constructs(
  composite("SIC", multi_items("sic_", 1:7), weights = mode_B),
  composite("PL", multi_items("pl_", 1:4)),
  composite("PIC", multi_items("pic_", 1:5)),
  composite("PI", multi_items("pi_", 1:5)),
  composite("WTP", single_item("wtp")),
  composite("PQ", multi_items("pq_", 1:4))
  )

```

# * Model comparisions *

```{r}

# Create structural models

# Model 1

sm_1 <- relationships(
  paths(from = c("SIC","PL","PQ","PIC"), to = "PI"),
  paths(from = "PI", to = "WTP"),
  paths(from = "SIC", to = c("PL","PQ")))

plot(sm_1)
```

```{r}

# Model 2

sm_2 <- relationships(
  paths(from = c("SIC","PL","PQ","PIC"), to = "PI"),
  paths(from = "PI", to = "WTP"),
  paths(from = "SIC", to = c("PL","PQ","PIC")))

plot(sm_2)
```

```{r}
# Model 3

sm_3 <- relationships(
  paths(from = c("SIC","PL","PQ","PIC"), to = "PI"),
  paths(from = "PI", to = "WTP"),
  paths(from = "SIC", to = c("PL","PQ","PIC","WTP")))

plot(sm_3)
```

# * Estimate and summarize the models *

```{r}

#Model 1

pls_model1 <- estimate_pls(
  data = influencer_data,
  measurement_model = measurement_model,
  structural_model = sm_1,
  missing_value = "-99"
)
```

```{r}
sum_model1 <- summary(pls_model1)

```

```{r}

#Model 2

pls_model2 <- estimate_pls(
  data = influencer_data,
  measurement_model = measurement_model,
  structural_model = sm_2,
  missing_value = "-99"
)
```

```{r}
sum_model2 <- summary(pls_model2)
```

```{r}

#Model 3

pls_model3 <- estimate_pls(
  data = influencer_data,
  measurement_model = measurement_model,
  structural_model = sm_3,
  missing_value = "-99"
)
```

```{r}
sum_model3 <- summary(pls_model3)
```

```{r}
# Inspect the IT Criteria matrix of Model1

sum_model1$it_criteria

```

```{r}
# Subset the matrix to only return the BIC row and PQ column

sum_model1$it_criteria["BIC", "PQ"]

```

```{r}
# Collect the vector of BIC values for PQ

itcriteria_vector <- c(sum_model1$it_criteria["BIC","PQ"],
                       sum_model2$it_criteria["BIC","PQ"],
                       sum_model3$it_criteria["BIC","PQ"])
```

```{r}
# Assign the model names to IT Criteria vector

names(itcriteria_vector) <- c("Model1", "Model2", "Model3")

```

```{r}
# Inspect the IT Criteria vector for competing models
itcriteria_vector
```
# Here I can compare the IT criteria for the 3 models.


```{r}

# Calculate the model BIC Akaike weights

compute_itcriteria_weights(itcriteria_vector)

```

# Here I can compare the 3 models with BIC Akaike weights.

#--------------------------------------------------------------

# * MEDIATION *

```{r}

# Create measurement model

mm_med <- constructs(
  composite("SIC", multi_items("sic_", 1:7), weights = mode_B),
  composite("PL", multi_items("pl_", 1:4)),
  composite("PIC", multi_items("pic_", 1:5)),
  composite("PI", multi_items("pi_", 1:5)),
  composite("WTP", single_item("wtp")),
  composite("PQ", multi_items("pq_", 1:4))
  )

```

```{r}
# Create structural model

sm_med <- relationships(
  paths(from = c("SIC","PL","PQ","PIC"), to = "PI"),
  paths(from = "PI", to = "WTP"),
  paths(from = "PL", to = "WTP"),
  paths(from = "PQ", to = "PL"),
  paths(from = "PIC", to = "WTP"),
  paths(from = "SIC", to = c("PL","PQ")))


plot(sm_med)
```

```{r}
# Estimate the model

med_pls <- estimate_pls(data = influencer_data,
                                      measurement_model = mm_med,
                                      structural_model = sm_med,
                                      missing = mean_replacement,
                                      missing_value = "-99")

```

```{r}

# Summarize the results of the model estimation

summary_med <- summary(med_pls)

```

```{r}

# Bootstrap the model

boot_med <- bootstrap_model(
  seminr_model = med_pls,
  nboot = 1000,
  cores = parallel::detectCores(),
  seed = 123

)

```

```{r}
# Summarize the results of the bootstrap

summary_boot_med <- summary(boot_med, alpha = 0.05)

```


```{r}

# Inspect total indirect effects

summary_med$total_indirect_effects

```

```{r}
# Inspect indirect effects

specific_effect_significance(boot_med,
                             from = "PL",
                             through = "PI",
                             to = "WTP",
                             alpha = 0.05)
```
# Indirect effect of PL to WTP is insignificant.

```{r}
specific_effect_significance(boot_med,
                             from = "PIC",
                             through = "PI",
                             to = "WTP",
                             alpha = 0.05)

```
# Indirect effect of PIC to WTP is insignificant.

# As indirect effect is insignificant for both cases, there is surely No Mediation.
# But to identify what type of non - mediation it is , I will anlyze the direct effect.

```{r}
# Inspect the direct effects

summary_med$paths

```

```{r}
# Inspect the confidence intervals for direct effects

summary_boot_med$bootstrapped_paths

```
# Here direct effect of PL to WTP is significant. But, indirect effect is insignificant
# That means it is - direct only non mediation.


# Again, direct effect of PIC to WTP is insignificant. And also indirect effect is 
# insignificant. That means it is : no effect - no mediation.


# As there is no mediation there is no need to further evaluate if PI acts as a 
# complementary or competitive mediator.


#------------------------------------------------------------

# * MODERATION *

```{r}

# Create the measurement model

mm_mod <- constructs(
  composite("SIC", multi_items("sic_", 1:7), weights = mode_B),
  composite("PL", multi_items("pl_", 1:4)),
  composite("PIC", multi_items("pic_", 1:5)),
  composite("PI", multi_items("pi_", 1:5)),
  composite("WTP", single_item("wtp")),
  composite("PQ", multi_items("pq_", 1:4)),
  interaction_term(iv = "PQ", moderator = "PIC", method = two_stage))
```


```{r}

# Plot the measurement model

plot(mm_mod)

```

```{r}
# Create the structural model

sm_mod <- relationships(
  paths(from = c("PL","PQ","PIC", "PQ*PIC"), to = "PI"),
  paths(from = "PI", to = "WTP"),
  paths(from = "PL", to = "WTP"),
  paths(from = "PQ", to = "PL"),
  paths(from = "PIC", to = "WTP"),
  paths(from = "SIC", to = c("PL","PQ", "PI")))

```


```{r}

# Plot the structural model

plot(sm_mod)

```


```{r}
# Estimate the new model with moderator

mod_pls <- estimate_pls(data = influencer_data,
                                      measurement_model = mm_mod,
                                      structural_model = sm_mod,
                                      missing = mean_replacement,
                                      missing_value = "-99")
```

```{r}
# Extract the summary

summery_mod <- summary(mod_pls)

```

```{r}
# Bootstrap the model
boot_mod <- bootstrap_model(
  seminr_model = mod_pls,
  nboot = 1000)
```

```{r}
# Summarize the results of the bootstrap

sum_boot_mod <- summary(boot_mod, alpha = 0.05)

```

```{r}
# Inspect the bootstrapped structural paths

sum_boot_mod$bootstrapped_paths

```
# Here all of them are insignificant except - PL to PI , PL to WTP , PQ to PL ,

# SIC to PL and SIC to PQ

```{r}

# Simple slope analysis plot

slope_analysis(
  moderated_model = mod_pls,
  dv = "PI",
  moderator = "PIC",
  iv = "PQ",
  leg_place = "bottomright"
  )

```


# Here, the 3 lines showing the relationship between PQ and PI. The middle line represents

# the average level.
